Workstat

### 2023-02-24 FEM_R/variable_testing/workstat.Rmd
Started a directory for variable testing in R. Added script for workstat and physically_active

---
title: "R Notebook"
output: html_notebook
---

ROUGH WORK CHECKING SCRIPT FOR LONELINESS AND SOCIAL ISOLATION WORK.

@@

## NEW PHYSICALLY_ACTIVE

```{r}
# First long file
physact.long <- long %>% 
  select(idauniq, wave, age, male, educ, workstat, employed, inactive, retired,
         physically_active) %>%
  replace_na(list(physically_active = -9)) %>%
  group_by(wave, physically_active) %>%
  summarise(n = n(), 
            age.mean = mean(age, na.rm=TRUE),
            age.median = median(age, na.rm=TRUE),
            age.5064 = sum(age >= 50 & age < 65, na.rm=TRUE),
            age.6579 = sum(age >= 65 & age < 80, na.rm=TRUE),
            age.80p = sum(age > 79, na.rm=TRUE),
            male.prop = (sum(male, na.rm=TRUE) / n),
            female = (n - sum(male, na.rm=TRUE)),
            educ.mean = mean(educ, na.rm=TRUE),
            educ1 = sum(educ == 1, na.rm=TRUE),
            educ2 = sum(educ == 2, na.rm=TRUE),
            educ3 = sum(educ == 3, na.rm=TRUE),
            workstat.mean = mean(workstat, na.rm=TRUE),
            employed = sum(employed, na.rm=TRUE),
            inactive = sum(inactive, na.rm=TRUE),
            retired = sum(retired, na.rm=TRUE))

physact.long$wave <- as.integer(physact.long$wave)
physact.long$physically_active <- as.factor(physact.long$physically_active)
```

#### By Age

```{r}
ggplot(data = physact.long, aes(x = wave, y = n, group = physically_active, colour = physically_active)) +
  geom_line() +
  scale_x_continuous(breaks=c(1:9)) +
  labs(title = 'Number') +
  xlab('Wave') +
  ylab('Count')

ggplot(data = physact.long, aes(x = wave, y = age.mean, group = physically_active, colour = physically_active)) +
  geom_line() +
  scale_x_continuous(breaks=c(1:9)) +
  labs(title = 'Mean Age') +
  xlab('Wave') +
  ylab('Count')

age.groups <- physact.long %>% 
  select(wave, physically_active, age.5064, 
                                      age.6579, age.80p) %>%
  pivot_longer(cols = age.5064:age.80p,
               names_to = 'age_group',
               values_to = 'count')

ggplot(data = age.groups, aes(x = wave, y = count, group = physically_active, colour = physically_active)) +
  geom_line() +
  scale_x_continuous(breaks=c(1:9)) +
  facet_grid(age_group ~ .) +
  labs(title = 'Count by Age Group') +
  xlab('Wave') +
  ylab('Count')

# ggplot(data = physact.long, aes(x = wave, y = age.mean, group = physically_active, colour = physically_active)) +
#   geom_line() +
#   scale_x_continuous(breaks=c(1:9)) +
#   labs(title = 'Mean Age') +
#   xlab('Wave') +
#   ylab('Count')
```

#### By Sex

```{r}
ggplot(data = physact.long, aes(x = wave, y = male.prop, group = physically_active, colour = physically_active)) +
  geom_line() +
  scale_x_continuous(breaks=c(1:9)) +
  labs(title = 'Number') +
  xlab('Wave') +
  ylab('Count')
```

#### By Educ

### Job Physically Active

New variable being used to determine physically active var above. Just want to 
plot and see.

```{r}
# First long file
jphysl.long <- long %>% 
  select(idauniq, wave, age, male, educ, workstat, employed, inactive, retired,
         jphysl) %>%
  group_by(wave, jphysl) %>%
  summarise(n = n(), 
            age.mean = mean(age),
            age.median = median(age),
            age.5064 = sum(age >= 50 & age < 65),
            age.6579 = sum(age >= 65 & age < 80),
            age.80p = sum(age > 79),
            male = sum(male),
            female = (n - sum(male)),
            educ.mean = mean(educ),
            educ1 = sum(educ == 1),
            educ2 = sum(educ == 2),
            educ3 = sum(educ == 3),
            workstat.mean = mean(workstat),
            employed = sum(employed),
            inactive = sum(inactive),
            retired = sum(retired))

jphysl.long$wave <- as.integer(physact.long$wave)
```

```{r}
ggplot(data = jphysl.long, aes(x = wave, y = count)) +
  geom_line() +
  scale_x_continuous(breaks=c(1:9)) +
  labs(title = 'Workstat in ELSA') +
  xlab('Wave') +
  ylab('Count')
```

## NEW WORKSTAT

@@

```{r}
# First long file
test.CV1 <- long %>% 
  select(idauniq, wave, workstat, l2workstat, employed, 
         inactive, retired, l2employed, l2inactive, l2retired) %>%
  group_by(wave) %>%
  summarise(employed = sum(employed),
            inactive = sum(inactive),
            retired = sum(retired)) %>%
  pivot_longer(cols = employed:retired,
               names_to = 'workstat',
               values_to = 'count')

```{r}
ggplot(data = test.long, aes(x = wave, y = count, group = workstat, color=workstat)) +
  geom_line() +
  scale_x_continuous(breaks=c(1:9)) +
  labs(title = 'Workstat in ELSA') +
  xlab('Wave') +
  ylab('Count')
```

>>>>

---
title: "Workstat"
output: html_notebook
---

@@

@@
